Interactive results review

### 2024-07-30 nbs/guides/interactive/interactive.qmd
fix(nbs): indicate explicit output
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

```{python}
# | label: load-postprocessed-data
import scanpy as sc
from pyrovelocity.utils import print_anndata

@@

```{python}
# | label: load-posterior-samples
from pyrovelocity.utils import pretty_print_dict
from pyrovelocity.io import CompressedPickle

>>>>

```{python}
# | label: load-postprocessed-data
# | output: true
import scanpy as sc
from pyrovelocity.utils import print_anndata

@@

```{python}
# | label: load-posterior-samples
# | output: true
from pyrovelocity.utils import pretty_print_dict
from pyrovelocity.io import CompressedPickle
